---
title: "Peer-graded Assignment: R Markdown and Leaflet"
author: "Manuel Alejandro Jiménez Torres"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: no
    toc_float: yes
    theme: cosmo
    keep_md: no
    df_print: paged
  pdf_document:
    toc: yes
    df_print: kable
    number_sections: false
    fig_caption: yes
    highlight: tango
    dev: pdf
  word_document:
    toc: yes
    df_print: paged
    keep_md: no
---

## Summary

This web page corresponds to the first assignment of the Developing Data Products course offered through Coursera from Johns Hopkins University.

The repository of the work can be found at the following link: <a target="_blank" href="https://github.com/alejimdro/R-Markdown-and-Leaflet">Developing Data Products_Assignment 1</a>

## Description

In my opinion, as a family or with friends, the indicated places are the most suitable to spend a pleasant moment. All these places offer chicken, that's the reason for the image.

The page was built in **RStudio** using **R Markdown and the Leaflet** package to build an interactive map.

```{r setup, include = FALSE}
# set knitr options
knitr::opts_chunk$set(echo = TRUE, fig.path = 'figures/')
# clear the global workspace (including hidden objects)
rm(list = ls(all.names = TRUE))
# set working directory
setwd("https://github.com/alejimdro/R-Markdown-and-Leaflet")
# free up memory and display statistics on free memory
gc()
```

```{r hot-wing-locations-map, message = FALSE, echo = TRUE}
library(knitr)
library(leaflet)
hwIcon <- makeIcon(
  iconUrl = "Figures/food-people.png",
  iconWidth = 25,
  iconHeight = 50
)
hwLocations <- data.frame(name = c("The Flame BBQ",
                                   "The Sports Grille Cranberry",
                                   "Kings Family",
                                   "El Campesino"),
                          lat = c(40.684667,
                                  40.68623,
                                  40.45082,
                                  40.867617),
                          lng = c(-80.109943,
                                  -80.101728,
                                  -80.182565,
                                  -79.922441))
hwPopup <- c(
  "<a href = 'http://theflamebbq.com/' target = '_blank'>The Flame BBQ</a>",
  "<a href = 'https://www.thesportsgrillecranberry.com/' target = '_blank'>The Sports Grille Cranberry</a>",
  "<a href = 'https://www.kingsfamily.com/' target = '_blank'>Kings Family</a>",
  "<a href = 'https://elcampesinopgh.com/' target = '_blank'>El Campesino</a>"
)
hwLocations %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hwIcon, popup = hwPopup)
```